Untitled

### 2024-02-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
abstract updated

MUR 3) *Multi-attribute instrument tools* that: (i) attaches structured metadata about an instrument (e.g. name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) applies a pre-written (for AQol-6D and EQ-5D instruments) or user-supplied instrument scoring function to a human records dataset; and (iii) generates descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).

@@

MUR 5) *Utility mapping reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific summary manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a single consolidated study reproducibility program that implements all steps inclusive of data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.

@@

### Application
We have previously described a study [@Hamilton2021.07.07.21260129] that used applied these modules and reporting templates to develop utility mapping models in a sample of young people presenting to primary mental health services. We used these module libraries to write programs that reproduced that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstratehow to applying the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821]. We also created an open access study input parameters and results dataset [@DVN/DKDIB0_2021]) and toy datasets to help demonstrate the transferability of the study algorithm [@DVN/HJXYKQ_2021]).

@@

## Documentation website
We created a documentation website (https://readyforwhatsnext.org/) using functions from our foundation framework library to partially automate content updates relating to available modules, datasets and analysis programs.

## Transferability assessment
We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against <!-- Edit_start -->our TRU criteria <!-- Edit_end -->. For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.  We believe our utility mapping study modules have satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and have partially met one criterion (U2). The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries authored as part of this study.

>>>>

MUR 3) *Multi-attribute instrument scoring tools* that: (i) attach structured metadata about an instrument (e.g. name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) apply pre-written (for AQol-6D and EQ-5D instruments) or user-supplied instrument scoring functions to a human records dataset; and (iii) generate descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).

@@

MUR 5) *Utility mapping study reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific summary manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a single consolidated study reproducibility program that implements all steps inclusive of data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.

@@

### Application
We have previously described a study [@Hamilton2021.07.07.21260129] that used applied these modules and reporting templates to develop utility mapping models in a sample of young people presenting to primary mental health services. We used these module libraries to write programs that reproduced that study's reporting and analysis algorithm [@hamilton_matthew_2022_6129906], to demonstrate how to applying the utility mapping models constructed in that study to new data [@hamilton_matthew_2022_6416330] and to generate a synthetic representation of the study dataset [@hamilton_matthew_p_2022_6321821]. We also created an open access study input parameters and results dataset [@DVN/DKDIB0_2021]) and toy datasets to help demonstrate the transferability of the study algorithm [@DVN/HJXYKQ_2021]).

@@

## Documentation website
We used using the search and documentation tools from our foundation framework library to
create and help maintain a documentation website (https://readyforwhatsnext.org/) that includes details on available model modules, datasets and analysis programs and tutorials on using model modules.

## Transferability assessment
We subjectively assessed these utility mapping model artefacts against <!-- Edit_start -->our TRU criteria <!-- Edit_end --> (Table \@ref(tab:checktb)). For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.  We believe our utility mapping study modules have satisfactorily met four of the six criteria (T1, R1, R2 and U1) and have partially met two criteria (T2 and U2). The main shortcomings that we identified when applying the assessment criteria was that we have yet to: (i) ensure that module library documentation includes examples of how to apply all exported methods and functions; and (ii) adequately implement unit testing.

### 2024-02-25 Markdown/Manuscript/Child_RMDs/MS_Tables_4.Rmd
abstract updated

                               "T2 Project team contributions and judgments are easily identified", 
                               "R1 Programming practices promote generalisability and transferability",
                               "R2 Licenses restrict only unethical reuse",

@@

                               "U2 New releases are systematically retested and deprecated"),
                 `Met?` = c(rep("Yes",5),"Partial"),

@@

                            "All module libraries, programs, and datasets are distributed with citation information. Public GitHub repositories detail author code contributions over project development history. Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes. Each code library is documented with worked examples of how to apply CHEM modules.  Analysis and reporting programs are self-documenting.  Sub-routines for generating reports are documented with README files.",

>>>>

                               "T2 Developer contributions and judgments on appropriate use are easily identified", 
                               "R1 Programming practices promote selective reuse",
                               "R2 Licenses permit derivative works",

@@

                               "U2 Releases are systematically retested and deprecated"),
                 `Met?` = c("Yes","Partial",rep("Yes",3),"Partial"),

@@

                            "All module libraries, programs, and datasets are distributed with citation information. Public GitHub repositories detail author code contributions over project development history. Model catalogues persistently available on the Harvard Dataverse describe the predictive performance of models under multiple usage regimes. Each code library is documented with worked examples of how to apply CHEM modules. However, documentation of individual functions and methods need more examples. Analysis and reporting programs are self-documenting. Sub-routines for generating reports are documented with README files.",
